Probabilistic Multiclass Kernel Embedding Classifier

### 2017-04-16 kernel_embedding_classifier.tex
Add draft for sections 2, 3, 4, 5, 8, 9

@@

	\subsection{Stochastic Gradient Descent}
	\label{sec:stochastic_gradient_descent}

		With standard gradient descent, the time complexity of each training iteration is dominated by the Cholesky decomposition of the regularised gram matrix $K_{\theta} + n \lambda I$ of size $n \times n$, which has a time complexity of $O(n^{3})$. In order to scale the hyperparameter training of kernel embedding classifiers to large dataset, we propose to optimise the complexity objective with stochastic gradient descent.

@@

		\begin{proof}
			For convergence in $\ell_{1}$, we simply extend \cref{thm:probability_convergence}, which proved that each entry of $\hat{\bvec{p}}(x)$ converges stochastically at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$. The $\ell_{1}$-norm distance is simply

@@

			It is straight forward to show if each term in the sum converges stochastically at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, then so does the sum, which proves the convergence in $\ell_{1}$.

@@

			where the last equality comes from \eqref{eq:rkhs_norm_is_l2_norm} and the fact that the empirical and true conditional embeddings are bounded functions in the RKHS. Since this is true for all $x \in \mathcal{X}$, the convergence is pointwise uniform.
		\end{proof}

>>>>

		\note{Note: The proof can just stop right here really. Every time we have some estimator error being upper bounded by some constant (in this case, $1$) times the RKHS norm of the difference between the empirical and true conditional embeddings, we can simply say that if the right hand side goes to zero at a stochastic rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, then so does the left hand side. The constant needs to be independent of $n \in \mathbb{N}_{+}$ for this to be true. If the constant is independent of $x \in \mathcal{X}$, then the convergence is uniform. If not, then the convergence is non-uniform.}

@@

	\subsection{Mini-Batch Stochastic Gradient Descent}
	\label{sec:stochastic_gradient_descent}

		With standard gradient descent, the time complexity of each training iteration is dominated by the Cholesky decomposition of the regularised gram matrix $K_{\theta} + n \lambda I$ of size $n \times n$, which has a time complexity of $O(n^{3})$. In order to scale the hyperparameter training of kernel embedding classifiers to large datasets, we propose to optimise the complexity objective with stochastic gradient descent.

		We begin by selecting a mini-batch size $n_{b} << n$ that is much smaller than $n$. The objective \eqref{eq:trace_norm_optimisation} is then computed only for the mini-batch

@@

		\begin{proof}
			For convergence in $\ell_{1}$, we simply extend \cref{thm:probability_convergence}, which proved that each entry of $\hat{\bvec{p}}(x)$ converges pointwise uniformly at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ to the corresponding entry of $\bvec{p}(x)$. The $\ell_{1}$-norm of the difference is simply

@@

			Since each term in the sum converges stochastically at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, then so does the sum, which proves the pointwise uniform convergence in $\ell_{1}$.

@@

			where the last equality comes from \eqref{eq:rkhs_norm_is_l2_norm} and the fact that the empirical and true conditional embeddings are bounded functions in the RKHS. Since this is true for all $x \in \mathcal{X}$ and the rate does not depend on $x \in \mathcal{X}$, the convergence is pointwise uniform.
		\end{proof}
